% This file was converted to LaTeX by Writer2LaTeX ver. 1.4
% see http://writer2latex.sourceforge.net for more info
\documentclass{article}
\usepackage[ascii]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage{array}
\usepackage{supertabular}
\usepackage{hhline}
\makeatletter
\newcommand\arraybslash{\let\\\@arraycr}
\makeatother
\setlength\tabcolsep{1mm}
\renewcommand\arraystretch{1.3}
\title{}
\begin{document}
\begin{flushleft}
\tablefirsthead{}
\tablehead{}
\tabletail{}
\tablelasttail{}
\begin{supertabular}{|m{1.1899999cm}|m{2.294cm}|m{3.827cm}|m{4.086cm}|m{1.573cm}|m{10.45cm}|}
\hline
Test number &
Description &
Data Type  &
Expected Result &
Pass/Fail &
Cross Reference\\\hline
1 &
Checking that the login screen allows user to log in with their credentials. &
Typical &
System logs in using the user's data. &
Pass &
Image 1\newline
Image 2\\\hline
2 &
Checking that the log in screen does not allow people to log in with any credentials. &
Erroneous.\newline
(Incorrect Password) &
Error message appears.\newline
(Your Username or Password is incorrect. Please try again.) &
Pass &
~

~

Image 3\\\hline
3 &
Checking that the program calculates `k' correctly. &
Typical.

(6.42\^{}-1, 5.15\^{}-1, 1, 1, 4.12\^{}-4) &
Answer ~calculated using correct steps ~and being the same as on a calculator (rounded to 3sigfig). &
~

Pass &
~

image 4

image 5\\\hline
4 &
Checking that the program accepts correct answers for `k' values. &
Typical &
Answer

rounded to 3 sig fig and entered in the correct format opens ``correct answer'' message box. &
~

Pass &
~

~

~

image 6 image 7\\\hline
5 &
Checking that the program accepts correct answers for `k' values. &
Erroneous (any incorrect answer, sdfdgido, 9.25\^{}-5). &
Answer given compared to the correct answer, then ``incorrect answer'' message box opened. &
Pass &
~Image 8 image 9 image 10\\\hline
6 &
That an account must have a unique username, cannot have any unfilled fields apart from middle name and that a target grade between A-U. &
Typical

(Student,Jack,William,Montfort,salmon,JMontfort, 12EJP, A) &
Student account allowed to be made, ``new student created'' message box opened. &
Pass &
~Image 11

~
\\\hline
7 &
Testing that accounts are saved when created. &
Data entered in last test. &
Correct student account details printed out. &
Pass &
Image 12 image 13\\\hline
8 &
Checking that only valid information can be input into the fields. &
Erroneous

(Target grade correct as this is picked up, but the rest are not). &
Student account not made, error message displayed. &
Pass &
Image 14\\\hline
9 &
Clicking the ``Practise Questions'' button opens the ``Practise Questions'' window. &
Typical

(clicking the correct button) &
Practise questions window opens. &
Pass &
Imagie 15\\\hline
10 &
That total population has to be bigger than the amount of heterozygous individuals when making a Hardy-Weinberg question. &
Erroneous

(Larger homozygous recessive,300, than total population , 32) &
Question is not allowed to be created, error message opens. &
Pass &
Image 16\\\hline
11 &
That total population has to be bigger than the amount of heterozygous individuals when making a Hardy-Weinberg question. &
Typical (total pop 32, no of homozygous recessive 10) &
Question allowed to be created, confirmation message box. &
Pass &
~

image 17\\\hline
12 &
That questions are stored correctly in questions.pickle &
Data from last test &
Correct question details printed from pickle. &
Pass &
~

image 18

~\\\hline
13 &
Testing that questions can be added to a QSet, that duplicate questions can't be added and that QSets can be saved if they fit the correct criteria. &
Typical(1 : Hardy-Weinberg, 2 : Rate Constant) &
Selected fields move to the ``New Set'' box, questions cannot be moved to the ``New Set'' box if they are already in the ``New Set'' box. A message box opens saying that a question set has been . &
Pass &
19 20 21\\\hline
14 &
Testing that a QSet is saved. &
Typical(1 : Hardy-Weinberg, 2 : Rate Constant) &
Correct QSet details printed out. &
Pass &
~

22\\\hline
15 &
Test that a QSet must have a name to be created &
No name entered. &
Error message opens and QSet is not saved. &
Pass &
~~~~~~~~~~~~~~~~~ 23\\\hline
16 &
Test that a QSet must have questions in it to be created. &
No questions put in ``New Set'' box &
Error message opens and QSet is not saved. &
Pass &
24\\\hline
17 &
~ &
~ &
~ &
~ &
~\\\hline
\end{supertabular}
\end{flushleft}

\bigskip

~

~

~

~

~

~lol

~

~

~

~

~

~

~

~

~

~

~

~

~

~

~

~

~


\bigskip
\end{document}
